---
title: "Copilot Trial 1"
output: 
  html_document:
    code_folding: show
    theme:
      bg: "#202123"
      fg: "#B8BCC2"
      primary: "#EA80FC"
      secondary: "#00DAC6"
      base_font:
        google: Prompt
      heading_font:
        google: Proza Libre
---

### Initial Experiments with Copilot for R In VSCode

```{r}
x <- rnorm(n = 10, mean = 1, sd = 1)

x
```

```{r}
# Generate 200 samples from normal distribution N(10, 5)
# and plot a histogram of the samples
x <- rnorm(n = 200, mean = 10, sd = 5)
hist(x, col = "blue", main = "Histogram of x", xlab = "x values")
```


```{r}
# get the life expectancy and gdp data from gapminder
library(gapminder)
gapminder <- gapminder
```

```{r}
# summarize the data in gapminder
summary(gapminder)
```

First Suggestion/Response from Copilot (to initiating a function def with its name)

```{r}
CalculateDaysBetweenTheDates <- function(date1, date2) {
  # calculate the number of days between two dates
  # date1 and date2 are character strings in the format "YYYY-MM-DD"
  # returns the number of days between the two dates
  date1 <- as.Date(date1)
  date2 <- as.Date(date2)
  return(as.numeric(date2 - date1))
}
```

```{r}
CalculateDaysBetweenTheDates("1955-08-12", "2023-06-21")
```

```{r}
CalculateWeeksBetweenTheDates <- function(date1, date2) {
  # calculate the number of weeks between two dates
  # date1 and date2 are character strings in the format "YYYY-MM-DD"
  # returns the number of weeks between the two dates
  date1 <- as.Date(date1)
  date2 <- as.Date(date2)
  return(as.numeric(date2 - date1) / 7)
}
```

```{r}
CalculateWeeksBetweenTheDates("1955-08-12", "2023-06-21")
```

#### Seeing Alternative Suggestions

> If alternative suggestions are available,
you can see these alternatives by pressing Alt+. (or Alt+,).

```{r}
```

#### Generating code suggestions from comments

> You can describe something you want to do using natural language within a comment, 
and GitHub Copilot will suggest the code to accomplish your goal.